\section{Global motion inferred from the streamer}
The kinematic information inferred from the streamer fitting provides constraints not only on the local velocity structure, but also on the global dynamical state of the infalling envelope. In particular, the characteristic spatial scale of the collapse $r_{\rm s}$ derived from the model represents a scaling radius that sets the relative importance of gravity and thermal pressure gradient, and governs the radial dependence of the velocity and density structure of the infalling envelope. For all four sources analyzed in this study, the best-fit values of $r_{\rm s}$ are significantly larger than the radial extent of the observed streamer structures (Table~\ref{table:best_fit_core_properties}). This indicates that the streamers are situated entirely within the free-fall regime of the envelope, where gravity dominates over thermal support. As a result, the overall streamer kinematics are consistent with freefall motion, despite the presence of curvature and velocity gradients introduced by angular momentum. This result highlights the importance of three--dimensional modeling in interpreting streamer dynamics. While projected position--velocity signatures alone may not uniquely reveal free-fall behavior, the inferred model parameters demonstrate that the observed streamers trace gas undergoing gravitational collapse toward the central star--disk system.

\section{Envelope accretion rates and the role of streamers}
Our model allows an estimate of the mass accretion rate associated with the large-scale envelope collapse feeding the star--disk systems. When inferred from our model fitting, the resulting envelope-to-disk accretion of class 0/I YSOs is systematically larger than the accretion rates previously attributed to individual streamers alone (see Section~\ref{sec:Mass_Accretion_Rate_and_Rotational_Energy}). This comparison suggests that, while streamers may trace localized channels of infalling material, their contribution to the overall disk mass budget is likely subdominant, and they may not significantly alter the global disk structure.

\section{Implications of inconsistent inclination}
In this work, the inclination derived from the streamer fitting represents the angular momentum vector orientation of the large-scale infalling envelope traced by the streamer, whereas literature values of disk inclination are typically obtained from continuum emission or molecular-line observations. When disk inclinations are available, the streamer-derived inclination can therefore be directly compared with the disk orientation after accounting for the geometric conversion between the model and observational reference frames. In these four sources, we find that the inclination inferred from the streamer kinematics differs from the disk inclination reported in the literature. Such discrepancies may indicate a misalignment between the angular momentum of the inner disk and that of the larger-scale envelope, which can naturally arise if the angular momentum of the collapsing core varies with radius. Alternatively, projection effects and uncertainties in tracing different physical components may also contribute to the observed differences. These inclination inconsistencies suggest that streamers may preserve information about the dynamical state of the envelope on larger scales, which is not necessarily aligned with the orientation of the inner disk. As a result, our streamer model provides a complementary probe of the three-dimensional accretion geometry beyond what can be inferred from disk observations alone.

\section{Model limitations and alternative interpretations}
In the cases where the model fails to reproduce the observed streamer morphology or kinematics, this discrepancy may indicate that the underlying structure arises from physical processes not captured by the current framework, such as alternative formation mechanisms or interactions beyond simple gravitational collapse and rotation. In some cases, it is indeed possible that streamers reflect clumpy accretion from outside of the core that gets elongated under the tidal forces. This kind of streamer can contribute more importantly to mass accretion, which is usually the case for Class II objects and later. Otherwise, overdensity is also often observed along the walls of outflow cavities, which has completely different origin compared to what is presented here. These cases highlight the limitations of the model and motivate further investigation into the diversity of streamer origins.

Although the present model is primarily designed to describe streamer formation in embedded systems where a substantial envelope is still present, the inner free-fall solution may also be applicable to certain cases of late-time, clumpy accretion onto an isolated or weakly embedded disk. In such scenarios, overdense clumps accreted from the surrounding environment can be stretched into elongated, streamer structures by the gravitational potential of the central star--disk system. Interestingly, we find that the model provides a reasonable description of the streamer kinematics in S~CrA, despite its more evolved nature. This suggests that, while the physical origin of streamers may differ between embedded and more evolved systems, the resulting kinematic signatures in the inner free-fall regime can be similar, allowing a unified modeling approach to capture key aspects of their dynamics.

\section{Data treatment and partially constrained parameters}
We further compare fitting results obtained using moment maps with those derived from the full spectral data cube (e.g., Per-emb-2). While moment maps provide a compact representation of the emission morphology, they inevitably discard information along the velocity axis. In contrast, fitting based on the full data cube retains the complete position--position--velocity structure, enabling a slightly more accurate reconstruction of both the projected streamer geometry and the line-of-sight velocity field.

For parameter that is partially constrained by previous observations, such as the disk inclination, we adopt a conservative approach by treating as free parameter in the fitting procedure. On the other hand, it is also possible to fit only some of the parameters among the five when the others are very well-constraint through other measurements. This allows the model to independently recover the preferred geometric configuration, which can then be directly compared with literature values, rather than enforcing prior assumptions that could bias the inferred solution.

\section{Robustness of MCMC}
During the MCMC exploration, we occasionally encounter runs that terminate abnormally or converge unrealistically fast. These cases are characterized by near-zero acceptance fractions, undefined or NaN autocorrelation times, and extremely short execution times, indicating that the ensemble of walkers fails to effectively explore the parameter space. Such behavior most likely arises when walkers become trapped in regions of vanishing posterior probability, which can be caused by overly restrictive priors, numerical instabilities in the likelihood evaluation, or strong parameter correlations that effectively collapse the sampling onto a lower-dimensional subspace. In contrast, successful MCMC runs exhibit longer execution times, acceptance fractions within the expected range, and well-defined autocorrelation times, reflecting efficient sampling of the posterior distribution. We therefore interpret runs with vanishing acceptance rates and undefined convergence diagnostics as non-converged and exclude them from further analysis, retaining only chains that demonstrate stable sampling behavior and statistically meaningful convergence.