\section{The formation of cores}
Stars form within cold, dense regions of molecular clouds, where local density enhancements can initiate gravitational collapse. Once a sufficiently overdense region begins to contract, it forms a dense core, a gravitationally bound structure that represents the earliest stage of star formation. Before any central heating source develops, the collapsing dense core is referred to as a prestellar core, characterized by low temperatures ($\sim$10 K) and the absence of an internal heat source.

As the collapse proceeds and densities rise, the gas eventually becomes optically thick to its own radiation. At this point, radiative cooling becomes inefficient, and the collapse slows as the pressure begins to increase adiabatically. This transition leads to the formation of the first hydrostatic core (FHSC), which is a short-lived structure supported primarily by adiabatic pressure. The FHSC phase lasts only a few thousand years and marks a key evolutionary stage between the prestellar core and the protostellar core.

When the temperature in the center increases to ≳2000 K, molecular hydrogen begins to dissociate, a process that absorbs energy and reduces thermal pressure support. This triggers a second, rapid collapse and gives rise to the protostar, the central object that continues to grow by accreting material from its surrounding envelope. Although accretion from the envelope begins during the prestellar and FHSC stages, the protostar phase formally begins once the second collapse produces a gravitationally bound central object.

The envelope surrounding the forming protostar is a cold, dusty reservoir of infalling material. It typically extends over thousands to tens of thousands of AU, and in the earliest stages the envelope retains a large fraction of the system's mass.

During the early Class 0 and Class I stages, the protostar remains enshrouded within this parental envelope. In this turbulent and gravitationally unstable environment, small perturbations within the envelope can grow nonlinearly, giving rise to asymmetric, filamentary overdensities known as streamers. These streamers represent dense structures within the infalling envelope and, unlike the rotationally supported disk, do not necessarily follow Keplerian motion. They are increasingly recognized as an important channel for transporting material from the envelope onto the disk, thereby influencing disk growth, stability, and angular-momentum redistribution.

Over time, as accretion weakens and the envelope dissipates, the protostar evolves into a pre-main-sequence star, eventually contracting toward the main sequence where sustained hydrogen fusion begins.
\section{The streamer in observations}
Recently, several observations revealed asymmetric structures in the protostellar system (e.g., \citealt{Pineda_2020}, \citealt{Valdivia-Mena_2022}, \citealt{Hsieh_2023}). The features of streamers are very diverse in morphology, do not always form in a disk plane, and have very weak density enhancement in observation. 

\section{Observations}
To test our model against sources where streamers have been detected, we use five observational datasets: Per-emb-2, Per-emb-50, S CrA, HL Tau, and SVS 13A. The Per-emb-2, Per-emb-50, and SVS 13A were observed by the Northern Extended Millimeter Array (NOEMA). Per-emb-2 was observed in D-configuration on June 22, July 27-28, and August 19, 2018, and in C-configuration on October 9, 10, 17, and 18 (project S18AG, \citealt{Pineda_2020}). The baseline values ranged from 16.4 to 287.8 meters. Per-emb-50 was observed in C-configuration on December 29, 2019, and January 5, 2021, and D-configuration on August 6, September 7, and 8, 2020 (\citealt{Valdivia-Mena_2022}). SVS13A was also observed using two different configurations: C-configuration on December 29, 2019, and January 5, 2020, and in D-configuration on August 6 and September 7, 2020. The baseline range is between 15.6 and 368 meters, corresponding to a synthesized beam size of $1.^"2 \times 0.^"7$ (\citealt{Hsieh_2023}). The S CrA , HL Tau were observed by Atacama Large Millimeter/submillimeter Array (ALMA). The S CrA observation data from ALMA Science Archrive was observed on November 6, 2019 (Project 2019.1.01792.S, \citealt{Gupta_2023}). HL Tau was observed by ALMA's C40-7 array configuration on August 22, 28, and September 1, 2017. The maximum projected baseline length is ~3.3 km (\citealt{Yen_2019}). For each source, we extract the position-position-velocity (PPV) data of the streamer.

\subsection{Per-emb-2}

\subsection{Per-emb-50}

\subsection{SVS 13A}

\subsection{S CrA}

\subsection{HL Tau}

\section{Our work overview}
The formation process of protoplanetary disks is still unrefined. Given their importance, we have developed a new model to characterize the streamer features and kinematics, focusing on gravitationally driven infalling and rotation.

